Fluid structure interaction with ETVF

### 2021-05-04 manuscript/paper.tex
Make fsi coupling scheme agnostic to structures. Add dam break examples
GTVF fsi scheme added. No results though.

\section{Fluid structure coupling}
\label{sec:fsi-coupling}

@@

>>>>

\section{Governing equations}

\subsection{Discrete governing equations}

In this current paper the fluid medium is modelled using the improvised scheme
of TVF, which is been applied to the free surface flows, called ETVF.

For detailed derivation we point the reader to paper \cite{cite our paper},
here we only give the discrete equations.

The discretized equations of the fluid medium are

\begin{equation}
  \label{eq:sph-discretization-continuity}
  \frac{\tilde{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; (
  \rho_{a} \; \tilde{\ten{u}}_{ab} \; + \;
  (\rho \; (\tilde{\ten{u}} \; - \;
  \ten{u}))_{ab}) \; \cdot \nabla_{a} W_{ab},
\end{equation}

\begin{multline}
  \label{eq:sph-discretization-edac}
  \frac{\tilde{d}p_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; \bigg(
  (p_{a} - \rho_{a} c_{s}^2) \; \ten{u}_{ab} \; - \;
  p_{a} \; \tilde{\ten{u}}_{ab} \; - \;
  (p \; (\tilde{\ten{u}} - \ten{u}))_{ab} \; + \; \\
  4 \; \nu_{edac}
  \frac{p_a - p_b}{(\rho_a + \rho_b) (r^2_{ab} + EPS)} \ten{r}_{ab}
  \bigg) \; \cdot \nabla_{a} W_{ab}
\end{multline}

\begin{multline}
  \label{eq:sph-momentum-fluid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}\bigg) \bigg]
  \nabla_{a} W_{ab} \\
  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot \nabla_{a} W_{ab} +
  \ten{g}_{a}.
\end{multline}

\begin{equation}
  \label{eq:sph-momentum-solid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\teng{\sigma}^{'}_{a}}{\rho_a^2} +
  \frac{\teng{\sigma}^{'}_{b}}{\rho_b^2}\bigg) \bigg]  \nabla_{a} W_{ab} +
  \ten{g}_{a}.
\end{equation}

The Jaumann's formulation for Hooke's stress provides us with the rate of
change of deviatoric stress,
\begin{equation}
  \label{eq:jaumann-stress-rate}
  \frac{d \sigma'_{ij}}{dt} = 2G (\dot{\epsilon}_{ij} - \frac{1}{3}
  \dot{\epsilon}_{ij} \delta_{ij}) + \sigma^{'}_{ik}  \Omega_{jk} +
  \Omega_{ik} \sigma^{'}_{kj}
\end{equation}
where $G$ is the shear modulus, $\dot{\epsilon}_{ij}$ is the strain rate tensor,
\begin{equation}
  \label{eq:strain-tensor}
  \dot{\epsilon}_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} +
  \frac{\partial u_j}{\partial x_i} \bigg)
\end{equation}
and $\Omega_{ij}$ is the rotational tensor,
\begin{equation}
  \label{eq:rotational-tensor}
  \Omega_{ij} = \frac{1}{2} \bigg(\frac{\partial u_i}{\partial x_j} -
  \frac{\partial u_j}{\partial x_i} \bigg)
\end{equation}

\begin{equation}
  \label{eq:sph-vel-grad}
  \nabla \ten{u}_a =
  - \sum_{b} \frac{m_b}{\rho_{b}} (\ten{u}_{a} - \ten{u}_{b}) \otimes (\nabla_{a} W_{ab}),
\end{equation}

In both fluid and solid modelling, the pressure is computed using an
isothermal equation of state, given as,
\begin{equation}
  \label{eq:pressure-equation}
  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
\end{equation}
where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
$\rho_0$ are the reference speed of sound and density, respectively.

\subsection{Boundary conditions}

\subsection{Time integration}

\subsection{Coupling between fluid and solid}
\label{subsec:fsi-coupling}

@@

\subsection{Hydrostatic water column on an elastic plate}
\label{sec:hydrostatic-water-column-on-an-elastic-plate}

In the current simulation a total of two particle spacing is used. One with
$\delta x = 0.04 , 0.02m and 0.01 m$ and use quintic spline as a kernel. We
use 1e-6, 1e-7 for timestepping of fluid, solid phases respectively. All the
simulations are run for a total time of $t_f = 1e-4s$. In figures XXX, XXX,
XXX we show the final positions of the particles with different particle
resolutions. The fluid contours are pressure and the structure contours is the
y-displacement. In figure XXX we plot the midpoint deflection with time and
compare it with the analytical solution provided by khayyer. It can be seen
that the results produced by the current scheme are accurate and validates the
scheme for further use in FSI problems. We have run a convergence analysis
with a reducing spacing and as can be seen in the figure, that as the particle
spacing is reduced the error is reduced.
